Optimal (Multiway) Spatial Joins

### 2024-05-25 msj.tex
yufei

        \item Consider any $k$-tuple $(r_1, r_2, ..., r_{k-2}, h, v) \in \J_2$. Let $h'$ be the trimmed segment of $h$, and set $\bm{t} = (r_1, ..., r_{k-3}, h', v)$. Then, $\bm{t} \in \J(R_1, ..., R_{k-3}, H', V)$ and $h' \in \contained_{R_{k-2}}(\bm{t})$.

@@

\extraspacing {\bf Set $\bm{H^*}$.} Fix any $i \in [k-2]$. For each segment $h' \in H'$, define
\myeqn{
    \minleft(h') &=& \min_{v \in V: h' \cap v \ne \emptyset} \text{$x$-coordinate of $v$}. 
}
We set $\minleft(h')$ to $\infty$, if $h'$ intersects no segment in $V$. When $\minleft(h') \ne \infty$, assuming $h' = [x_1, x_2] \times y$, we introduce a horizontal segment
\myeqn{
    h^* &=& [x_1, \minleft(h')] \times y. \nn
}
and call it the {\em minimal segment} of $r'$.

@@

Next, we construct from $H'$ a new set of rectangles: 
\myeqn{
    H^* = \set{h^* \mid h' \in H' \text{ and its minimal segment $h^*$ exists}}. \label{eqn:hv:type2:H*}
}
Computing $H^*$ from $H'$ and $V$ is an instance of Problem $\mathscr{B}$, and can be achieved in $O(n \log n)$ as per the discussion from Section~\ref{sec:bricks}.

>>>>

        \item Consider any $k$-tuple $(r_1, ..., r_{k-2}, h, v) \in \J_2$. Let $h'$ be the trimmed segment of $h$, and set $\bm{t} = (r_1, ..., r_{k-3}, h', v)$. Then, $\bm{t} \in \J(R_1, ..., R_{k-3}, H', V)$ and $h' \in \contained_{R_{k-2}}(\bm{t})$.

@@

\extraspacing {\bf Set $\bm{H^*}$.} 
For each segment $h' \in H'$, define
\myeqn{
    \minleft(h') = \min_{\substack{\text{$\bm{t} \in \J(R_1, ..., R_{k-3}, H', V):$}\\ \text{$\bm{t}[k-2] = h'$}}} \text{$x$-coordinate of $\bm{t}[k-1]$}. 
    \label{eqn:minleft}
}
We reminder the reader that, in the above equation, $\bm{t}[k-2]$ is a horizontal segment and $\bm{t}[k-1]$ is a vertical segment. We set $\minleft(h')$ to $\infty$, if no $\bm{t} \in \J(R_1, ..., R_{k-3}, H', V)$ has $h'$ in its field $\bm{t}[k-2]$. When $\minleft(h') \ne \infty$, assuming $h' = [x_1, x_2] \times y$, we introduce a horizontal segment
\myeqn{
    h^* &=& [x_1, \minleft(h')] \times y. \nn
}
and call it the {\em minimal segment} of $h'$.

@@

Next, we construct from $H'$ a new set of horizontal segments: 
\myeqn{
    H^* = \set{h^* \mid h' \in H' \text{ and its minimal segment $h^*$ exists}}. \label{eqn:hv:type2:H*}
}
Computing $H^*$ from $H'$ and $V$ is an instance of Problem $\mathscr{B}$, and can be achieved in $O(n \log n)$ as per the discussion from Section~\ref{sec:bricks}.
